\documentclass[10pt,oneside]{article}

% language setup
\usepackage[english]{babel}

% margins
\usepackage[left=1.5in, right=1.75in, top=1in, bottom=0.75in]{geometry}% adjust the page margins

\RequirePackage{xcolor}
\definecolor{DartGreen}{HTML}{006633} % official Dartmouth Green color -- use for headers
\definecolor{DartAccent}{HTML}{66cc33} % official Dartmouth accent -- use for urls
\definecolor{BlueAccent}{HTML}{55cee6} % background color, blue accent -- do not use for anything else
\definecolor{BlueAccent}{HTML}{55cee6} % backup color 
\definecolor{GrassGreen}{HTML}{359245}
\definecolor{WarmYellow}{HTML}{E9A139}
%% Choose fonts for use with xelatex


% Better footer
\usepackage{fancyhdr}
\fancyhf{}
\fancyfoot[L]{Current as of \today}
\fancyfoot[R]{\thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{1pt}
\pagestyle{fancy}


\usepackage{fontspec}
\setromanfont[
	Path = ../fonts/,
  UprightFont = *-Regular,
	BoldFont = *-Bold,
	ItalicFont = *-Italic,
	BoldItalicFont = *-BoldItalic,
	Extension = .ttf,
]{Lato}
\setsansfont[
	Path = ../fonts/,
  UprightFont = *-Regular,
	Extension = .ttf,
]{Inconsolata}

% Section styling
\usepackage{titlesec}
\titlespacing*{\section}{2cm}{1ex}{0.25in}
\titleformat{\section}[leftmargin]{\raggedleft\sffamily\footnotesize\bfseries}{}{0pt}{\color{DartAccent}}

\makeatletter
\newif\ifaftersec\aftersecfalse

\newcommand\setsubskip{%
    \global\aftersectrue
    \everypar{%
        \global\aftersecfalse
        \if@noskipsec
            \global\@noskipsecfalse
            \clubpenalty\@M
            \hskip-\parindent
            \begingroup
                \@svsechd\unskip{\hspace{\@tempskipb}}%
            \endgroup
        \else
            \clubpenalty\@clubpenalty\everypar{}%
        \fi}}

\newcommand\subskip{%
  \ifaftersec
     \removelastskip%
     \vspace{-\baselineskip}
  \fi
  \global\aftersecfalse}


% Subsection styling
\titleformat{\subsection}{\subskip\itshape}{}{0pt}{}[]
\titlespacing*{\subsection}{0em}{0.5ex}{0ex}

\raggedbottom

% useful macro
\newcommand{\dotspace}{\quad}

% better lists
\usepackage{enumitem}
\setlist[itemize, 1]{nosep, noitemsep, labelsep=-5pt, leftmargin=*, after=\vspace{\baselineskip}, itemindent=-15pt, labelindent=5pt}

% fixed width tables
\usepackage{array}
\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
\newcolumntype{C}[1]{>{\PreserveBackslash\centering}p{#1}}
\newcolumntype{R}[1]{>{\PreserveBackslash\raggedleft}p{#1}}
\newcolumntype{L}[1]{>{\PreserveBackslash\raggedright}p{#1}}

\usepackage[autostyle=true, autopunct=true, english=american]{csquotes}

\usepackage[
	backend=biber,
	style=publist,
	plauthorfirstinit=true,
	plauthorhandling=highlight,
	plnumbered=false,
	labeldateparts=false,
	linktitles={none, doi, url},
	hlyear=true,
	marginyear=false,
	doi=true,
	url=false,
	isbn=false,
	maxbibnames=99,
	maxcitenames=99,
  giveninits,
	date=year
]{biblatex}
\renewbibmacro{in:}{}
\setlength{\bibhang}{15pt}

% remove period inbetween volume and number
\renewbibmacro*{volume+number+eid}{%
  \printfield{volume}%
%  \setunit*{\adddot}% DELETED
  \setunit*{\addnbspace}% NEW (optional); there's also \addnbthinspace
  \printfield{number}%
  \setunit{\addcomma\space}%
  \printfield{eid}%
}

\AtEveryBibitem{%
  \clearlist{language}%
}

% add bib resources
\addbibresource{../bibliography/my-papers.bib}
\addbibresource{../bibliography/conferences.bib}

% bold my name
\plauthorname[Adam]{Pollack}
\plauthorname[Adam B]{Pollack}
\plauthorname[A]{Pollack}

% include everything in bibliography
\nocite{*}

%% other stuff
% icons for the contact info
\usepackage{fontawesome5}
\usepackage{academicons}

% got this from here https://www.reddit.com/r/LaTeX/comments/40zflc/embedding_url_link_into_article_title_using/
\newbibmacro{string+doi}[1]{%
  \iffieldundef{doi}{\iffieldundef{url}{#1}{\href{\thefield{url}}{#1}}}{\href{http://dx.doi.org/\thefield{doi}}{#1}}}
\DeclareFieldFormat*{title}{\usebibmacro{string+doi}{\mkbibemph{#1}}}

% have to load this last
\usepackage{hyperref} % Required for adding links	and customizing them
\hypersetup{hidelinks, breaklinks, urlcolor=DartAccent, linkcolor=DartAccent}

%---------------------------------------------------------------------

\begin{document}

\thispagestyle{empty}
%% Name and contact block
\noindent{
  \footnotesize
  \color{DartGreen}
  \begin{tabular}{L{0.5\textwidth}R{0.5\textwidth}}
    Dartmouth College       & \texttt{\href{mailto:adam.b.pollack@dartmouth.edu}{adam.b.pollack@dartmouth.edu}} \, \faEnvelope                                                                                  \\
    Thayer School of Engineering       & \texttt{\href{https://abpoll.github.io/}{https://abpoll.github.io/}} \, \faGlobe                                                                                                \\
    Hinman 8000, 15 Thayer Dr    & \texttt{\href{https://github.com/abpoll}{abpoll}} \, \faGithub                                                                      \\
    Hanover, NH 03755 & \texttt{\href{https://scholar.google.com/citations?user=mnigw6AAAAAJ}{Adam Pollack}} \, \aiGoogleScholar \\
  \end{tabular}
}

\bigskip

%% Name
\noindent{\LARGE\bfseries \textcolor{DartGreen}{Adam Pollack}}
\reversemarginpar

\bigskip

%% Research Interests

\section{research interests}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\begin{itemize}[label={}]
  
  \item Equity in climate risk management
        
  \item Values informed decision-making under uncertainty
        
  \item Flood risk dynamics in housing markets
        
  \item Uncertainty in flood risk valuation and estimation
        
  \item Reproducibility and usefulness of scientific practices
        
\end{itemize}

%% Appointments

\section{appointments}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\begin{itemize}[label={}]
  
  \item \textbf{Dartmouth College}
        
        \textit{Research Scientist}, Thayer School of Engineering, 2024--present.
        
        
        \textit{Postdoctoral Research Associate}, Thayer School of Engineering, 2022--2024.
        
        adviser: Klaus Keller
        
        
        
\end{itemize}

%% Education

\section{education}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\begin{itemize}[label={}]
  
  \item \textbf{Boston University}
        
        \textit{Ph.D}, Earth \& Environment, 2022.
        
        
        dissertation: Flood Risk Valuation and Estimation from County to Continental Scales
        
        advisers: Christoph Nolte and Ian Sue Wing
        
        
  \item \textbf{Stony Brook University}
        
        \textit{M.S.}, Applied Mathematics and Statistics, 2017.
        
        \textit{B.S.}, Applied Mathematics and Statistics, 2016.
        
        
        
\end{itemize}

%% Grants and Contracts

\section{grants and contracts}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\begin{itemize}[label={}]
  
  \item \textbf{Co-Principal Investigator}, \enquote{Contribute to the Integrated Coastal Modeling (ICoM) project, Subaward to Dartmouth College from Battelle}.  PI: Klaus Keller. {DOE-Prime}, \$231,794. 2023--2024.
        
\end{itemize}

%% Publications

\section{journal articles}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}
\vspace*{-1em}

\uspunctuation

\printbibliography[type=article, heading=none]

\section{preprints \& in review}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}
\vspace*{-1em}
\printbibliography[type=unpublished, heading=none]

\section{technical reports}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}
\vspace*{-1em}
\printbibliography[type=report, heading=none]

\section{science translation}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}
\vspace*{-1em}
\printbibliography[type=misc, heading=none]

%% Invited Talks

\section{invited talks}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\begin{itemize}[label={}]
  
  \item \enquote{\textbf{Quantifying and managing climate risks and inequitable outcomes}}, School of Earth, Environment and Sustainability Invited Seminar,  \textit{University of Iowa}. , 2024.
  
  \item \enquote{\textbf{Improving equity considerations in multisector dynamics research}}, 2024 Energy Modeling Forum Snowmass Workshop,  \textit{Department of Energy, Biological and Environmental Research}. Snowmass, Colorado, 2024.
  
  \item \enquote{\textbf{Funding rules that promote equity in climate adaptation outomces}}, Faculty Seminar Series Talk,  \textit{The Arthur L. Irving Institute for Energy and Society at Dartmouth}. Hanover, New Hampshire, 2024.
  
  \item \enquote{\textbf{Funding rules that promote equity in climate adaptation outomces}}, University of Rhode Island Spring 2024 Seminar,  \textit{Department of Environmental and Natural Resource Economics}. Kingston, Rhode Island, 2024.
  
  \item \enquote{\textbf{Reproducible science is a foundation of convergence research}}, MACH Seminar Series,  \textit{Megalopolitan Coastal Transformation Hub (MACH)}. Online, 2024.
  
  \item \enquote{\textbf{Transparency on underlying values is needed for useful equity measurements}}, Working Group on Social-Science Water Research Invited Seminar Talk,  \textit{Helmholtz Centre for Environmental Research GmbH - UFZ}. Online, 2024.
  
  \item \enquote{\textbf{An Uncertain Structure and Fragility Ensemble (UNSAFE) for Flood Risk Assessments}}, Bi-Monthly ICoM-MSD Seminar Series,  \textit{Integrated Coastal Modeling project, Pacific Northwest National Laboratory}. Online, 2024.
  
  \item \enquote{\textbf{CoPe Cross-Hub Community of Practice: Successes and struggles on the path to convergence research}}, CoPe Cross-Hub Community of Practice Seminar,  \textit{National Science Foundation}. Online, 2023.
  
  \item \enquote{\textbf{Equity and Deep Uncertainty in Benefit Cost-Analyses Deep Dive}}, Annual Meeting of the Megalopolitan Coastal Transformation Hub,  \textit{Rutgers University-Camden}. Camden, New Jersey, 2023.
  
  \item \enquote{\textbf{Supporting Integration Through MACH Prototype Decision-Analyses}}, Integration Meeting of the Megalopolitan Coastal Transformation Hub,  \textit{Rutgers University}. Online, 2022.
  
  \item \enquote{\textbf{Using Toy Problems to Improve Intuition, Convergent Research Designs, and Decision-Support}}, Seminar Meeting of the Megalopolitan Coastal Transformation Hub,  \textit{Rutgers University}. Online, 2022.
  
  \item \enquote{\textbf{Do markets price weather-related risks?}}, Climate Econometrics Seminar Series,  \textit{Climate Econometrics, Nuffield College, University of Oxford}. Online, 2021.
  
  \item \enquote{\textbf{Can property level flood losses be reliably predicted?}}, First Street Foundation Flood Lab Workshop,  \textit{First Street Foundation}. Online, 2021.
  
  \item \enquote{\textbf{Flood Loss Risk and Its Drivers: Evidence from Massachusetts Residential Properties}}, 2020 Climate and Health Seminar,  \textit{Boston University School of Public Health}. Online, 2020.
  
  \item \enquote{\textbf{Parcel level flood risk and interventions in Massachusetts}}, Cloud to Street Lab Meeting,  \textit{Cloud to Street}. Online, 2020.
  
\end{itemize}

%% Conference Presentations
\section{conference presentations}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}
\vspace*{-1em}
\printbibliography[type=inproceedings, keyword={presentation}, heading=none]

%% Conference Posters
\section{conference posters}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}
\vspace*{-1em}
\printbibliography[type=inproceedings, keyword={poster}, heading=none]

%% Media Coverage

\section{media coverage}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\begin{itemize}[label={}]
  
  \item \href{https://cdn2.assets-servd.host/thayer-web/production/images/Dartmouth-Engineer-Magazine-Fall-2024.pdf?dm=1728076598}{Study Defines Equitable Approaches}, \textit{Catha Mayor}, \textbf{Dartmouth Engineer Magazine}, Fall 2024.
        
  \item \href{https://irving.dartmouth.edu/news/2025/01/building-bridges-theory-practice}{Building Bridges: From Theory to Practice}, \textit{Cate Homicki}, \textbf{The Arthur L. Irving Institute for Energy and Society Newsletter}, 2025-01-27.
        
  \item \href{https://eesm.science.energy.gov/news/msd-research-spotlight-adam-pollack}{MSD Research Spotlight: Adam Pollack}, \textit{Lillian Lau}, \textbf{MultiSector Dynamics Community newsletter}, 2024-07-19.
        
  \item \href{https://www.economist.com/graphic-detail/2023/04/25/accounting-for-flood-risk-would-lower-american-house-prices-by-187bn}{Accounting for flood risk would lower American house prices by \$187bn}, \textit{Graphic detail}, \textbf{The Economist}, 2023-04-25.
        
  \item \href{https://www.washingtonpost.com/climate-environment/2023/02/16/flood-risk-housing-market-property-value/}{Where U.S. house prices may be most overvalued as climate change worsens}, \textit{Brady Dennis}, \textbf{The Washington Post}, 2023-02-16.
        
  \item \href{https://www.bu.edu/articles/2020/will-bu-be-underwater-in-30-years-climate-change/}{Will BU Be Underwater in 30 Years?}, \textit{Rich Barlow}, \textbf{Boston University Today}, 2020-10-14.
        
\end{itemize}

%% Advising

\section{advising}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

%% \vspace{\baselineskip}


\subsection{Undergraduate}
\begin{itemize}[label={}]
%% 

\item Rainwater Harvesting User Study and Instrumentation Design. Thayer School of Engineering. Engs 89/90 Capstone Project Advisor. 2024--present.  

\item Elaine Sarazen. Thayer School of Engineering. Research Co-Mentor (with Klaus Keller). 2023--present.  

\item Daniel Xu. Quantitative Social Science \& Geography. Research Co-Mentor (with Klaus Keller). 2023--present.  

\item Julian Gutierrez. Thayer School of Engineering. Research Co-Mentor (with Klaus Keller). 2023--present.  

\item Camry Gach. Undeclared. WISP Research Internship Program Co-Mentor (with Klaus Keller). 2022--2023.  

\item Carter (Street) Roberts. Quantitative Social Sciences \& Environmental Studies. Research Co-Mentor (with Klaus Keller). 2022--2023.  

%% 
\end{itemize}


%% PEER REVIEW

\section{peer review}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\begin{itemize}[label={}]
  
    \item Business \& Economics
  
    \item Earth's Future
  
    \item Environmental Modelling \& Software
  
    \item Journal of Housing Economics
  
    \item Land Economics
  
    \item Natural Hazards
  
    \item Nature Communications
  
    \item Royal Society Open Science
  
    \item Water Resources Research
  
\end{itemize}

%% Awards

\section{awards}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\begin{itemize}[label={}]
  
  \item \textbf{Research Fellowship}, Boston University, 2022.
        
  \item \textbf{Research Fellowship}, Boston University, 2021.
        
  \item \textbf{Teaching Fellowship}, Boston University, 2021.
        
  \item \textbf{Research Fellowship}, Boston University, 2020.
        
  \item \textbf{Teaching Fellowship}, Boston University, 2020.
        
  \item \textbf{Research Fellowship}, Boston University, 2019.
        
  \item \textbf{Dean's Fellowship}, Boston University, 2019.
        
\end{itemize}

%% Teaching

\section{teaching}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}


\begin{itemize}[label={}]
  
  \item \textbf{Boston University}
        
        Data, Models and Analysis in Earth and Environment. Teaching Fellow and Lab Instructor. Spring 2021.
        
        Data, Models and Analysis in Earth and Environment. Teaching Fellow and Lab Instructor. Spring 2020.
        
        
  \item \textbf{Dartmouth College}
        
        How to produce FAIR analyses. Developed and Presented Teaching Module in Bayesian Statistical Modeling and Computation Course. Winter 2024.
        
        
  \item \textbf{Stony Brook University}
        
        Software Development Fundamentals. Teaching Assistant. Spring 2016.
        
        
\end{itemize}

%% Additional Experience and Training

\section{service}

\mbox{}\vspace{-\dimexpr\baselineskip\relax}

\begin{itemize}[label={}]
  
  \item \textbf{Member}, NSF Cross CoPe Student and Postdoc Planning Committee. 2024--present.
  
  \item \textbf{Social and Behavioral Research - Basic}, CITI program. 2022--2025.\\Record \#48549028.
  
  \item \textbf{Session Co-convener: Advances in Quantifying and Attributing Climate Impacts and Damages to Inform Climate Risk Management and Litigation}, 2024 American Geophysical Union Fall Meeting (Washington DC). 2024.
  
  \item \textbf{Technical Advisory Group Member}, Massachusetts’ Executive Office of Energy and Environmental Affairs Pluvial and Fluvial Flood Mapping. 2024.
  
  \item \textbf{Invited Panelist}, Dartmouth Feldberg Library Open Data Panel. 2024.
  
  \item \textbf{Abstract Reviewer}, Northeastern Agricultural Resource Economics Association. 2023--2024.
  
  \item \textbf{Notetaker and Rapporteur}, Multisectoral Dynamics Workshop Equity Breakout Sessions. 2023.
  
  \item \textbf{Co-Chair, Student Postdoc Leadership Council}, Megalopolitan Coastal Transformation Hub. 2022--2023.
  
  \item \textbf{Lead, Data Integration Working Group}, Megalopolitan Coastal Transformation Hub. 2022--2023.
  
  \item \textbf{Founder, Irving Institute Research Labs Seminar Group}, Irving Institute for Energy \& Society. 2022--2023.
  
  \item \textbf{Session Chair, Property Values (Flood Risk)}, Association of Environmental and Resource Economists 2020 Virtual Summer Conference. 2020.
  
\end{itemize}


\end{document}